\chapter{Plan}

So far I have begun the design of the website, as well as started to implement the first pitch detection function. I am aware that I have a lot left to do, so it is crucial that I plan my time correctly

\begin{itemize}
	\item 3rd of March - I will aim to have the basic skeleton of my website working including user log-in, and a rough pitch detection algorithm in place.
	\item 14th of March - Improve accuracy of pitch detection algorithm, and implement it into a "Note from Chord" exercise.
	\item Suspend progress until end of term on 28th due to exams!
	\item With the basic web interface designed, create multiple different exercises over Easter break until 26th of April and start getting users to test them. Start to experiment with creating adaptability in exercises to see how it can be done.
	\item 28th of April - REALITY CHECK, see where I've come, and where I still need to go. Re-evaluate rest of plan up until June accordingly.
	\item 1st of June Begin intensive user testing to gather information for my evaluation write up project simultaneously.
	\item 17th of June Final Report due.
\end{itemize}


\section{Extensions}
If I finish ahead of time, there are a couple of extensions that come to mind.
\begin{itemize}
	\item Support for MIDI instruments. There are a number of existing instruments you can plug straight into a PC using the MIDI to USB interface, it would be interesting to see how I could incorporate that into my project.
	\item Segmented crowd-sourced music transcription. Allow users to to test their music ability by playing them a short clip of music and getting them to supply information they've perceived about the segment, chord data, time signature data, melody data etc. The idea is that if enough users completed segments of a particular song, the song's structure could be pieced together.
\end{itemize}